---
title: "Glimpse Data"
author: "Saurabh"
date: "January 11, 2018"
output: html_document
---
#DATA from IHDS1 & 2
This is the phase1 of data importing

##Importing Data
```{r}
library(rio)
ihds1_hh <- import("22626-0002-Data.rda")

ihds2_hh <- import("36151-0002-Data.rda")
```


###Creating sid of data1 & data2 from StateId
```{r}
library(dplyr)
ihds1_hh$sid <- unlist(regmatches(ihds1_hh$STATEID,gregexpr("(*[0-9].)", ihds1_hh$STATEID)))

glimpse(ihds1_hh$sid)

ihds2_hh$sid <- gsub(".*[a-z|A-Z]\\s", "", ihds2_hh$STATEID)
glimpse(ihds2_hh$sid)
```

# Getting Unique HH Code
###Getting the Unique ID Variables ready for further process
```{r}
ihds1_hh$sid <- as.numeric(ihds1_hh$sid)
ihds2_hh$sid <- as.numeric(ihds2_hh$sid)
ihds1_hh$DISTID <- as.numeric(ihds1_hh$DISTID)
ihds2_hh$DISTID <- as.numeric(ihds2_hh$DISTID)
ihds1_hh$PSUID <- as.numeric(ihds1_hh$PSUID)
ihds2_hh$PSUID <- as.numeric(ihds2_hh$PSUID)
ihds1_hh$HHID <- as.numeric(ihds1_hh$HHID)
ihds2_hh$HHID <- as.numeric(ihds2_hh$HHID)
ihds1_hh$HHSPLITID <- as.numeric(ihds1_hh$HHSPLITID)
ihds2_hh$HHSPLITID <- as.numeric(ihds2_hh$HHSPLITID)
```

###Creating a new dataset of Unique Identifers
```{r}
library(dplyr)
ihds1_hh <- tbl_df(ihds1_hh)
ihds2_hh <- tbl_df(ihds2_hh)

id1 <- ihds1_hh %>%
  select(STATEID:IDHH, sid)

id2 <- ihds2_hh %>%
  select(STATEID:IDHH, sid)
```

###Formula
```{r}
id1$code <- id1$sid*10000000 + id1$DISTID*100000 + id1$PSUID*1000 + id1$HHID*10 + id1$HHSPLITID

id2$code <- id2$sid*10000000 + id2$DISTID*100000 + id2$PSUID*1000 + id2$HHID

glimpse(id1)
glimpse(id2)
```

###Attaching Unique code id to data
```{r}
ihds1_hh$code <- id1$code
ihds2_hh$code <- id2$code
```

###Survey id in IHDS 1 and 2
```{r}
ihds1_hh$SURVEY <- "1"

ihds2_hh$SURVEY <- gsub(".*[a-z|A-Z]\\s", "", ihds2_hh$SURVEY)
```

#Nrega specific data
```{r}
unique(ihds2_hh$IN16)

unique(ihds2_hh$NWKNREGA)

sum(ihds2_hh$NWKNREGA > 0)

summary(ihds2_hh$IN16)

sum(ihds2_hh$IN16 > 0, na.rm = TRUE)

sum(ihds2_hh$INCNREGA > 0)

table(ihds2_hh$IN25)
```
o/p1: So, we have got a max of 5 members in an HH who possess NREGA Jobcards
o/p2: A maximum of 5 members from the family have worked for NREGA in last one year
o/p3: We can see around 3311 HH have members worked for NREGA
o/p4: Summarizing the variable IN16 (No of Jobcards in a family) to understand no. of NA's. Unsbstantial amount: 74, can be ignored and can be considered as not working with NREGA
o/p5: No. of HHs who have jobcards
o/p6: No. of HHs who have got payed for NREGA
o/p7: No. of HHs who have worked for NREGA but still haven't got payed


###NREGA variable
```{r}
ihds1_hh$nrega <- FALSE

ihds2_hh$nrega <- ifelse(ihds2_hh$IN16 > 0, TRUE, FALSE)

sum(ihds2_hh$nrega, na.rm = TRUE)
```


#Data IHDS1 HH
```{r}
glimpse(ihds1_hh)
```


#Data IHDS2 HH
```{r}
glimpse(ihds2_hh)
```

