---
title: "EA 1.0"
author: "Saurabh"
date: "January 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We're considering data from Wave 1 and Wave 2

Before we could Quantify Nrega success, we need to understand the underlying occupation trends from the data.

District/State vs Income (Color = Religion, Shape = POOR, Size = HH Size)

```{r}
length(unique(ihds1_hh$DISTNAME))

head(unique(ihds1_hh$DISTNAME))
```


The class variable CG3 in IHDS 2 is not deduced from the collected data, but people themselves decide what class they lie in.

Let's create a class variable
```{r}
#UNderstanding the overall spread of Income variable
summary(ihds1_hh$INCOME)
```

```{r}
hist(ihds1_hh$INCOME/1000, breaks = 100)
```

Pretty clear that the data is skewed..
```{r}
car::Boxplot(ihds1_hh$INCOME)
```

Checking the outliers
```{r}
income1 <- (ihds1_hh[-c(3242, 3633, 5204, 24167, 26269, 28082, 30125, 32047, 34643, 9777, 38497, 15050, 26387,  3438, 38273,  1089, 37891, 41481, 36264), "INCOME"])

summary(income1)

```

How many people are more than annual INR 3 lakhs
```{r}
table(ihds1_hh$INCOME > 300000)
```

Again visualizing wrt the people with less than INR 3lakhs of Income
```{r}
library(magrittr)

income2 <- subset(ihds1_hh, INCOME < 300000) 

ggplot2::qplot(INCOME/1000, data = income2, binwidth = 10)
```
INcome of around 8000 approx observations lie between INR 3000 - INR 4000 

Understanding the position of these 8000 families wrt Poverty Line

```{r}
#How much was the poverty line?
head(ihds2_hh$POVLINE2012)
```



```{r}
head(ihds1_hh$POOR)

table(ihds1_hh$POOR)

```


```{r}
library(dplyr)

income1 <- tbl_df(income2)

class(income1)
```


```{r}
filter(income1, POOR == "(1) Yes") %>%
  summarise(poor = max(INCOME))

filter(income1, POOR == "(0) No") %>%
  summarise(non_poor = max(INCOME))
```



```{r}
library(ggplot2)

income1 %>%
ggplot(aes(x = NPERSONS, y = INCOME/100)) +
  geom_point(aes(shape = ID14, color = POOR), position = "jitter")


income1 %>%
  filter(POOR == "(1) Yes") %>%
  ggplot(aes(x = DISTNAME, y = INCOME/100))+
  geom_point(aes(shape = ID14, size = NPERSONS),position = "jitter") +
  scale_shape_manual(values = c(1:9))

```

```{r}
income1 %>%
  filter(POOR == "(0) No") %>%
  ggplot(aes(x = DISTNAME, y = INCOME/100))+
  geom_point(aes(shape = ID14, size = NPERSONS),position = "jitter") +
  scale_shape_manual(values = c(1:9)) +
  theme(axis.text.x = element_text(angle=70, hjust=1))
```

```{r}
table(ihds1_hh$ID14)
```

```{r}
table(ihds1_hh$ID13)
```

```{r}
table(ihds2_hh$ID13)
```

```{r}
table(ihds1_hh$GROUPS8)
```

```{r}
library(ggplot2)
library(dplyr)
ihds1_hh %>%
  ggplot(aes(x = STATEID, y = INCOME/100, fill = POOR)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle=70, hjust=1))

```

```{r}
library(dplyr)
library(ggplot2)
ihds2_hh %>%
  ggplot(aes(x = sid, y = INCOME/100, fill = POOR)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle=70, hjust=1))

```

Counting the number of HH in Dist and Dist in States
```{r}
hh_distribution <- cbind(aggregate(DISTID ~ STATEID, data = hh2, FUN = unique), table(hh2$sid))

hh_distribution

hh_distribution$Var1 <- NULL

hh_distribution$DISTID <- sapply(hh_distribution$DISTID, length)

names(hh_distribution) <- c("States", "Dist_freq", "HH_Freq")
```
```{r}
s2id <- table(hh2$DISTID, hh2$STATEID)

head(s2id)
s2id <- data.frame(s2id)

head(s2id)
dim(hh2)
```

Understanding the distribution of Total Agricultural land owned
```{r}
ihds1_hh %>%
  ggplot(aes(x = FM4)) +
  geom_histogram()
```

We can check the the proportion of farm income vs proportion of landowned and irrigated
```{r}
library(ggplot2)
ihds1_hh %>%
  ggplot(aes(x = FM4*FM2, y = INCFARM/300000)) +
  geom_jitter()
```

```{r}
summary(ihds1_hh$INCFARM)
```

```{r}
ihds1_hh[which(ihds1_hh$INCFARM == 3929000),]
```

