---
title: "Finding the discrepancy"
author: "Saurabh"
date: "January 19, 2018"
output: html_document
---


```{r}
id1 %>%
  select(code) %>%
  intersect(id2 %>%
              select(code))
```
36751 HH which are Intact as well as Split with HH "1" and Replaced HH "9"

Verifying that only Split Id has been included in the data!
```{r}
id2 %>%
  filter(HHSPLITID == 9) %>%
  select(HHSPLITID) %>%
  sum()
19206/2134    #The average comes to 9!!! No discrepancy in HHSPLITID as "9"
```


Tallying the frequency of each code under SplitID "9" 
```{r}
table09 <- id2 %>%
  filter(HHSPLITID == 9) %>%
  select(code) %>%
  table()

table09 <- tbl_df(table09)


table09
```


```{r}
names(table09) <- c("code", "freq")
table09$code <- as.numeric(table09$code)

table(table09$freq)
```
No discrepancy here!

Getting the intersect of codes with IHDS1
```{r}
id1 %>%
  select(code) %>%
  intersect(table09 %>%
              select(code))
```
###Voila!!!
So here, we get 2108 as the HH from IHDS1 which were replaced later in IHDS2. But there's a deficit of 26 observations.
See below....

```{r}
code09 <- id2 %>%
  filter(HHSPLITID == 9) %>%
  select(code)

code09
```

#Now I wish to find the deficit of 26HHs!
```{r}
discrepancy <- id1 %>%
  select(code) %>%
  intersect(table09 %>%
              select(code))

discrepancy
```

```{r}
code09_i <- which(id2$HHSPLITID == 9)
head(id2$code[code09_i])
code09_base <- id2$code[code09_i]
class(code09_base)
length(code09_base)

```
2134, Perfect!

```{r}
code_09_base2 <- tbl_df(code09_base)
names(code_09_base2) <- "code"

diff_discrepancy <- setdiff(code_09_base2, discrepancy)
diff_discrepancy
```
So now we get the difference between IHDS1 and IHDS2 for SPLITID "9"

Checking the HH in Rajasthan "08" and DistId "26". In both IHDS1 and IHDS2
```{r}
id1 %>%
  filter(sid == 08, DISTID == 26)
```
```{r}
id2 %>%
  filter(sid == 08, DISTID == 26)
```

What we've found out is that an altogether new replacement HH id was created in IHDS 2 see 82607111 (Not present in IHDS1)

Checking for Next observation:91006100, 160005240
First 91006100:

```{r}
id1 %>%
  filter(sid == 09, DISTID == 10)
```
There's no HHID 10!

```{r}
id2 %>%
  filter(sid == 09, DISTID == 10)
```

160005240
```{r}
id1 %>%
  filter(sid == 16, DISTID == 0)
```
Can't find 240!, we can see that HH 24 was coded as "1" for HHSPLITID, mostly an error... But we shall exclude it from the data.. :)
```{r}
id2 %>%
  filter(sid == 16, DISTID == 0)
```

Conclusion:
So we found out that 26 observations from IHDS 1 are not matching with Survey 2 for Replaced HH's
Is this the reason why we're getting SURPLUS of 26? Isn't it supposed to be a deficit?

