---
title: "Intersect1.1"
author: "Saurabh"
date: "January 17, 2018"
output: html_document
---

#Main Intersect between the 2 datasets
```{r}
ihds1_hh %>%
  select(code) %>%
  intersect(ihds2_hh %>%
              select(code))
```
There are 36751 Observation which are common in IHDS 1 and IHDS 2, these common observations include Split as well as Replaced HH. 
So we need to further dive into the dataset to get common non split as well as non replaced HHs

#Common HH from both the surveys excluding Replaced HH (HHSPLITID = 9)
```{r}
ihds1_hh %>%
  select(code) %>%
  intersect(ihds2_hh %>%
              filter(HHSPLITID != 9) %>%
              select(code))
```
We get 34643 HHs which are common, which might have split but doen't contain
Replaced HHs

#Common HH from both the surveys excluding Replaced HH as well as Non Split HH
###Non split HHs in IHDS II
We can find the intact HH via IHDS II
Technique: We can find the frequency of a certain HH code getting repeated by table function and filtering only those which have a frequency of 1.
```{r}
##Getting the frequency table
code_table <- table(as.character(ihds2_hh$code)) 
class(code_table)  
head(code_table)
```

```{r}
#Prepping the freq table for further assessment
code_table <- tbl_df(code_table)
names(code_table) <- c("code", "Freq")
code_table$code <- as.numeric(code_table$code)
code_table$Freq <- as.factor(code_table$Freq)
code_table

#Arranging codes in ascending order
code_table <- code_table[order(code_table$code),]
code_table
```
Above is an ordered frequency table coerced into a Tibble dataframe. 

###Estimated number of Non split HHs
```{r}
table(code_table$Freq)      #With Freq 1
```
We can see that there are 32596 HHs which have a frquency of 1, i.e. HHs which did not split at all, they may contain replaced HHs too

```{r}
#Tallying the count!
32596 + 3219*2 + 771*3 + 155*4 + 31*5 + 5*6   #Total HH

3219*2 + 771*3 + 155*4 + 31*5 + 5*6           #Total Split HH

dim(ihds2_hh)
```

###Understanding SPLITID Distribution in Survey 2
```{r}
table(ihds2_hh$HHSPLITID)
```

```{r}
4180 + 978 + 193 + 39 + 7 #= 5397
9556 - 5397 #= 4159 HHs in 34621 HHs are split HHs with Split Id "1" 
#Hence 
34621 - 4159 #= 30462
```



###Filtering the replaced HHs from the Freq table data

```{r}
tbl_df(code_table) %>%
  filter(Freq == 1) %>%
  select(code) %>%
  setdiff(ihds2_hh %>%
              filter(HHSPLITID == 9) %>%
              select(code))
```
When we remove Replaced HH we get 30462 HHs which are not split

#Understanding the NREGA Employees Distribution

```{r}
#Total Nrega employed HHs in IHDS2
summary(ihds2_hh$nrega)
```
In the sample of 42152 we have 11968 HHs which are employed under NREGA

```{r}
table(nrega = ihds2_hh$nrega, split = ihds2_hh$HHSPLITID)
```


#NREGA employed HHs which are Intact as well as not replaced

Now we'll be checking for those HHs which are enrolled under NREGA and are neither Split nor Replaced
```{r}
code_table %>%
  filter(Freq == 1) %>%
  select(code) %>%
  setdiff(ihds2_hh %>%
            filter(HHSPLITID == 9) %>%
            select(code)) %>%
  intersect(ihds2_hh %>%
              filter(nrega == TRUE) %>%
              select(code))
```
8850 HHs which are under NREGA and have neither split nor have been replaced.

```{r}
#Checking Specific Data which is TRUE for NREGA
View(ihds2_hh[which(ihds2_hh$code == 10202010),])
```

#Find NREGA Employed HHs from IHDS 2 in IHDS 1
Now using the above data we'll find out NREGA employed HHs frmo Data 2 in Data 1 
```{r}
code_table %>%
  filter(Freq == 1) %>%
  select(code) %>%
  setdiff(ihds2_hh %>%
            filter(HHSPLITID == 9) %>%
            select(code)) %>%
  intersect(ihds2_hh %>%
              filter(nrega == TRUE) %>%
              select(code)) %>%
  intersect(tbl_df(ihds1_hh %>%
                     select(code)))
```
So in all we have 8850 HHs which are common in Survey 1 and 2 and are those HHs which have neither split nor have been replaced.

#Summary:
36751 total common HH in IHDS 1 & IHDS 2 (Contains Split as well as replaced)
34643 common HH excluding replaced HHs only
32596 HHs in IHDS 2 which are intact (not split) but contain replaced HHs
30462 HHs in IHDS 2 which haven't split and doesn't have replaced HHs 
8850 HHs are NREGA employed as well as not split & not replaced in IHDS 2 as well as in the intersect of IHDS 1 and IHDS 2. 