---
title: "Interim_feedback"
author: "Saurabh"
date: "February 3, 2018"
output: html_document
---
Number of districts per state
```{r}
hh_nrega2 %>%
  group_by(stateid, distid) %>%
  summarise(n_hh = n_distinct(distid)) %>%
  summarise(nrega_dist = n()) %>%
  left_join(hh_non1 %>%
  group_by(stateid, distid) %>%
  summarise(n_hh = n_distinct(distid)) %>%
  summarise(non_nrega_dist = n()), by = "stateid")

```
What we don't know about the above districts is that are they the same districts distributed or are there two independent districts one with nrega and other with non_nrega

HH Nrega vs Non_nrega
```{r}
hh_prop_st <- hh_nrega2 %>%
  group_by(stateid) %>%
  summarise(hh_nrega = n()) %>%
    left_join(hh_non2 %>%
  group_by(stateid) %>%
  summarise(hh_non = n()), by = "stateid") %>%
  mutate(prop = round(hh_nrega/(hh_nrega + hh_non), 2))
hh_prop_st
```

```{r}
hh_prop_st %>%
  filter(prop > 0.30) %>%
  summarise(nrega_obs = sum(hh_nrega), non_obs = sum(hh_non))
```


Checking ids
```{r}
hh_nrega2 %>%
  select(sid, distid, psuid, hhid, hhsplitid, code)
```

```{r}
unique(hh_nrega2$hhsplitid)
unique(hh_non2$hhsplitid)
unique(hh_nrega$hhsplitid)
unique(hh_non$hhsplitid)
```
Though the codes uniqueness was checked we still have anomalies

```{r}
table(hh_nrega2$hhsplitid)
table(hh_non2$hhsplitid)
```

```{r}
code_final <- table(hh_nrega2$code)

code_final <- tbl_df(code_final)

head(code_final)
```

```{r}
code_final %>%
  filter(n == 1)
```
8850 codes are repeated just once, so even if they're anomalies there is chance that they're those entries which have split but the inital house is either untraceable in the database or hhsplitid is the classic example of an error entry.

```{r}
hhsplit2 <- hh_nrega2 %>%
  filter(hhsplitid == 2) %>%
  select(code, hhsplitid) 


semi_join(hh_nrega2, hhsplit2, by = "code")
```

```{r}
hh_nrega2 %>%
  filter(code == 20901100) %>%
  select (code, hhsplitid)
```

Checking the rest of the data too!!!
```{r}
table(hhx_new1$hhsplitid)
length(hhx_new1$hhsplitid)
table(hhy_new1$hhsplitid)
length(hhy_new1$hhsplitid)
table(hh_non2$hhsplitid)
length(hh_non2$hhsplitid)
table(hh_nrega2$hhsplitid)
length(hh_nrega2$hhsplitid)
```

```{r}
length(unique(hhx_new1$code))
length(unique(hhy_new1$code))
length(unique(hh_non2$code))
length(unique(hh_nrega2$code))
```
The codes are non repetitive, though we have other than 1 hhsplitids for few cases. Maybe we can live with those 6, 14 observations!!!


#Cluster Analysis
Getting the data for cluster!!
```{r}
x_subset <- hhx_new1 %>%
  select(copc, assets, fm20b, fm21a, fm22, fm23, fm24, fm26, fm27, fu1c, fu5b, fu6b, fu7b, fu8b, fu9b, fu10b) 

x_subset  
```
Desc Analysis of data
```{r}
#copc
desc_stat(x_subset$copc)
desc_stat(x_subset$assets)
```
1.)Need to replace NA's from copc to something more better, before replacing them we need to check if there are any outliers...
2.)Assets is good to go for next check as it has no NAs 

COPC
```{r}
boxplot(x_subset$copc)
```

```{r}
boxplot((x_subset[x_subset$copc < 10000,"copc"]))
```

```{r}
require(car)
require(dplyr)
require(ggplot2)

Boxplot(x_subset$copc)

```
Observing the outliers
```{r}
x_subset[c(26803, 7203, 4720, 1677, 10634, 13829, 1645, 28740, 29572, 21128),]
```

```{r}
Boxplot(x_subset$assets)
```

Checking the distribution of copc
```{r}
x_subset %>%
  filter(copc < 10000) %>%
  ggplot(aes(x=copc)) +
  geom_histogram()

x_subset %>%
  ggplot(aes(x=assets)) +
  geom_histogram()
```
 The distribution is absolutely skewed with maximum of observations lying in the first quarter of copc values.
What we need to see if the missing values and outliers come from specific state

All Outliers
```{r}
hhx_new1 %>%
  slice(c(26803, 7203, 4720, 1677, 10634, 13829, 1645, 28740, 29572, 21128)) %>%
  select(copc, district, stateid, assets)
```

All Na's
```{r}
hhx_new1 %>%
  slice(c(490, 491, 493, 494, 495, 500, 909, 1537, 2343, 2397, 2428,  2563, 2564, 2679,  3519, 3876, 3943, 4035, 4046, 4056, 5189,  5453, 5482, 5507, 5593, 5962, 6534, 8613, 10848, 13538, 18013, 18023, 18065, 18071, 18784, 19600, 20993, 21094, 27347)) %>%
  select(copc, district, stateid, assets)
```

```{r}
hhx_new1[-c(26803, 7203, 4720, 1677, 10634, 13829, 1645, 28740, 29572, 21128),] %>%
  group_by(stateid) %>%
  summarise(avg = mean(copc, na.rm = TRUE), median = median(copc, na.rm = TRUE), min = min(copc, na.rm = TRUE), max = max(copc, na.rm = TRUE))
```
Imputing NAs in accordance to state avg
```{r}
#NAs in Jammu
x_subset[c(490, 491, 493, 494, 495, 500), "copc"] <- 1157.0

#HP
x_subset[c(909, 1537), "copc"] <- 998.0

#Pb
x_subset[c(2343, 2397, 2428,  2563, 2564, 2679), "copc"] <- 966.5

#Hy
x_subset[c(3519, 3876, 3943, 4035, 4046, 4056), "copc"] <- 866.5

#Rj
x_subset[c(5189,  5453, 5482, 5507, 5593, 5962, 6534), "copc"] <- 641.5

#Up
x_subset[8613, "copc"] <- 551.0

#Tr
x_subset[10848, "copc"] <- 740.0

#Jh
x_subset[13538, "copc"] <- 448.0

#Mp
x_subset[c(18013, 18023, 18065, 18071), "copc"] <- 440.0

#Gj
x_subset[c(18784, 19600), "copc"] <- 787.0

#Mh
x_subset[c(20993, 21094), "copc"] <- 653.0

#Kr
x_subset[27347, "copc"] <- 658.5

any(is.na(x_subset$copc))
```


##Bivariate Analysis
```{r}
x_subset %>%
  filter(copc < 12500) %>%
  ggplot(aes(x = assets, y = copc)) +
  geom_point() + geom_smooth(model = "lm")



```

```{r}
which(x_subset$copc < 100)
```

```{r}
x_subset[which(x_subset$copc < 100),]
```

```{r}
hhx_new1 %>%
  filter(copc < 100) %>%
  select(stateid, district, copc, assets, npersons)
  
```

Removing NA's from other data!
```{r}
x_subset[which(is.na(x_subset$fm20b)), "fm20b"] <- 0
x_subset[which(is.na(x_subset$fm21a)), "fm21a"]<- 0
x_subset[which(is.na(x_subset$fm22)),"fm22"] <- 0
x_subset[which(is.na(x_subset$fm23)),"fm23"] <- 0
x_subset[which(is.na(x_subset$fm24)),] <- 0
x_subset[which(is.na(x_subset$fm26)),]  <- 0

x_subset[which(),]
is.na(x_subset$fm27) <- 0
x_subset[which(),]
is.na(x_subset$fu1c) <- 0
x_subset[which(),]
is.na(x_subset$fu5b) <- 0
x_subset[which(),]
is.na(x_subset$fu6b) <- 0
x_subset[which(),]
is.na(x_subset$fu7b) <- 0
x_subset[which(),]
is.na(x_subset$fu8b) <- 0
x_subset[which(),]
is.na(x_subset$fu9b) <- 0
x_subset[which(),]
is.na(x_subset$fu10b) <- 0

replace_na <- function(x,y) {
  for(i in x) {
    y <- recode(x,"NA = '0'") 
  }
}
library(car)
replace_na(x_subset$fm21a, x_subset$fm21a)

x_subset$fm21a <- recode(x_subset$fm21a, "NA = '0'")
x_subset$fm22 <- recode(x_subset$fm22, "NA = '0'")
x_subset$fm23 <- recode(x_subset$fm23, "NA = '0'")
x_subset$fm24 <- recode(x_subset$fm24, "NA = '0'")
x_subset$fm26 <- recode(x_subset$fm26, "NA = '0'")
x_subset$fm27 <- recode(x_subset$fm27, "NA = '0'")
x_subset$fu1c <- recode(x_subset$fu1c, "NA = '0'")
x_subset$fu5b <- recode(x_subset$fu5b, "NA = '0'")
x_subset$fu6b <- recode(x_subset$fu6b, "NA = '0'")
x_subset$fu7b <- recode(x_subset$fu7b, "NA = '0'")
x_subset$fu8b <- recode(x_subset$fu8b, "NA = '0'")
x_subset$fu9b <- recode(x_subset$fu9b, "NA = '0'")
x_subset$fu10b <- recode(x_subset$fu10b, "NA = '0'")
```

```{r}
head(x_subset, 20)
```

```{r}
library(fpc)
scale_x <- scale(x_subset[,c(1,2)])

cl_fpc <- kmeansruns(scale_x, krange = 2:10)
cl <- kmeans(scale_x[,c(1:2)], 3)
cl2 <- kmeans(scale_x, 4)
```

```{r}
cl$size
cl2$size
```

```{r}
x_subset$seg <- cl$cluster

x_subset %>%
  mutate(fm_exp = fm20b + fm21a + fm22 + fm23 + fm24 + fm26 + fm27, fu_exp = fu1c + fu10b + fu5b + fu6b + fu7b + fu8b + fu9b) %>%
  select(copc, assets, fm_exp, fu_exp, seg, -c(fm20b:fm27), -c(fu1c:fu10b)) %>%
  group_by(seg) %>%
  summarise(avg_copc = mean(copc), avg_assets = mean(assets), avg_fm = mean(fm_exp), avg_fu = mean(fu_exp))
```

```{r}
hhx_cl <- hhx_new1 %>%
  bind_cols(seg = cl$cluster)
```

```{r}
table(hhx_cl$seg, hhx_cl$poor)
```


```{r}
x_subset %>%
  ggplot(aes(y=copc, x = 1)) + 
  geom_boxplot() +
  facet_grid(~seg)
```


```{r}
x_subset2 <- x_subset[,-17]
x_subset2$seg <- cl2$cluster

x_subset2 %>%
  mutate(fm_exp = fm20b + fm21a + fm22 + fm23 + fm24 + fm26 + fm27, fu_exp = fu1c + fu10b + fu5b + fu6b + fu7b + fu8b + fu9b) %>%
  select(copc, assets, fm_exp, fu_exp, seg, -c(fm20b:fm27), -c(fu1c:fu10b)) %>%
  group_by(seg) %>%
  summarise(avg_copc = mean(copc), avg_assets = mean(assets), avg_fm = mean(fm_exp), avg_fu = mean(fu_exp))
```

```{r}
boxplot(copc~seg, x_subset2)
```

```{r}
hhx_cl$seg2 <- cl2$cluster
```

```{r}
table(hhx_cl$seg2, hhx_cl$poor)
```

