---
title: "New data"
author: "Saurabh"
date: "January 19, 2018"
output: html_document
---
The 30462 HH codes which haven't split and not replaced
```{r}
intact30k <- tbl_df(code_table) %>%
  filter(Freq == 1) %>%
  select(code) %>%
  setdiff(ihds2_hh %>%
            filter(HHSPLITID == 9) %>%
            select(code))
```


New dataframe with renamed variables
```{r}
new_hh2 <- cbind(cng_all2, fm_all2, fu_all2, in_all2, multi_all2, wa_all2, n_obs_all2, co_all2, cg_all2, hh_rc_all2, nf_all2, an_all2, me_all2, mp_all2, sa_all2, emp_all2)
```

Adding assets/jcard and jcard application variables in both data
```{r}
ihds1_hh$assets <- ihds1_hh$hhassets
ihds1_hh$jcard <- 0
ihds1_hh$jcardapp <- 0
new_hh2$jcard <- ihds2_hh$IN16
new_hh2$jcardapp <- ihds2_hh$IN17
```





```{r}
new_hh2 <- tbl_df(new_hh2)

head(new_hh2)
```

```{r}
hh_w2 <- merge(ihds1_hh, new_hh2, by = "code")
hh_w2 <- tbl_df(hh_w2)
```

```{r}
head(hh_w2)
```


```{r}
dim(hh_w2)
```
These are the obs with those 26 surplus less! But this is not the data which is expected. We would require, the 30k observations which are those HHs which didnot split and were not replaced.

Removing non common variables
```{r}
hh_wide <- hh_w2 %>%
  select(code, contains("."))
```

```{r}
dim(hh_wide)
```


```{r}
hhx <- hh_wide %>%
  select(code, contains(".x")) #%>%
  #bind_rows()
```



```{r}

hhx$groups8.x <- ifelse(hhx$groups8.x == "(1) Brahmin", "(1) Brahmin 1",
               ifelse(hhx$groups8.x == "(2) High caste", "(2) Forward caste 2",
                      ifelse(hhx$groups8.x == "(3) OBC", "(3) Other Backward Castes (OBC) 3",
                             ifelse(hhx$groups8.x == "(4) Dalit", "(4) Dalit 4",
                                    ifelse(hhx$groups8.x =="(5) Adivasi", "(5) Adivasi 5",
                                           ifelse(hhx$groups8.x == "(6) Muslim", "(6) Muslim 6", "(7) Christian, Sikh, Jain 7"))))))

summary(hhx$groups8.x)

summary(hhy$groups8.y)

```


```{r}
hhy <- hh_wide %>%
        select(code, contains(".y"))
```

```{r}
target <- names(hhx)
head(target)
class(target)
```
```{r}
target2 <- gsub("\\..*", "", x = target)
head(target2)
```


```{r}
hhx <- hhx[,order(names(hhx))]
head(hhx)
```

```{r}
hhy <- hhy[, order(names(hhy))]
hhy
```

Some cleaning of categorical vars
```{r}
levels(hhy$fm9b.y) <- unique(levels(hhx$fm9b.x))
levels(hhy$fm9c.y) <- unique(levels(hhx$fm9c.x))
```


```{r}
hhx_small <- merge(hhx, intact30k, by = "code") 
dim(hhx_small)
```


```{r}
unique(hhtest$hhsplitid.x)
```



```{r}
hhy_small <- merge(hhy, intact30k, by = "code")

head(hhy_small)
```

NOTE: Please check anomaly.rmd file!!!

```{r}
non_anomaly<-  hhy_small %>%
  select(code) %>%
  setdiff(anomaly)
dim(non_anomaly)
```

```{r}
hhx_small2 <- merge(hhx_small, non_anomaly, by = "code")
head(hhx_small2)
dim(hhx_small2)
```

```{r}
hhy_small2 <- merge(hhy_small, non_anomaly, by = "code")
dim(hhy_small2)
```

```{r}
#Just testing
table(hhy_small2$hhsplitid.y)
```

```{r}
setnames(hhx_small2, names(hhx_small2), gsub("\\..*", "", x = names(hhx_small2)))
head(hhx_small2)
```

```{r}
setnames(hhy_small2, names(hhy_small2), gsub("\\..*", "", x = names(hhy_small2)))
head(hhy_small2)
```


```{r}
test <- gsub("\\..*", "", x = hhx_small2)

head(test)
```

```{r}
hhx_small2 <- hhx_small2[,match(target2, names(hhx_small2))]
hhy_small2 <- hhy_small2[,match(target2, names(hhy_small2))]

```


```{r}
class(hhx_small2$idhh)
class(hhy_small2$idhh)
hhy_small2$idhh <- as.numeric(hhy_small2$idhh)

unique(hhx_small2$id20)
table(hhx_small2$id20)
unique(hhy_small2$id20)

head(hhy_small2$id20)
hhy_small2$id20 <- gsub(".*\\s", "", hhy_small2$id20)

table(hhy_small2$id20)
table(ihds2_hh$ID18C)
levels(hhy_small2$id20) <- c(0:16, 88)

class(hhy_small2$id20)
hhy_small2$id20 <- as.numeric(hhy_small2$id20)

levels(as.factor(hhx_small2$nf1a))
levels(hhy_small2$nf1a)
hhx_small2$nf1a <- NULL
hhy_small2$nf1a <- NULL

hhx_small2$nf10b <- NULL
hhy_small2$nf10b <- NULL

table(hhx_small2$co1b)
unique(hhy_small2$co1b)
hhx_small2$co1b <- factor(hhx_small2$co1b)
levels(hhx_small2$co1b) <- c("(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3", "15" )
levels(ihds2_hh$CO1B)
class(hhy_small2$co1b)
class(hhx_small2$co1b)

unique(hhy_small2$co2b)
unique(hhx_small2$co2b)
hhx_small2$co2b <- factor(hhx_small2$co2b)
levels(hhy_small2$co2b)
levels(hhx_small2$co2b) <- c("0", "(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3", "30")
table(hhx_small2$co2b)

unique(hhx_small2$co5b)
hhx_small2$co5b <- factor(hhx_small2$co5b)
levels(hhx_small2$co5b) <- c("0", "(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3")
unique(hhx_small2$co5b)

levels(hhy_small2$co5b)


hhx_small2$co7b <- factor(hhx_small2$co7b)
levels(hhx_small2$co7b) <- c("(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3", "4")
levels(hhy_small2$co7b)
table(hhx_small2$co7b)


hhx_small2$co8b <- factor(hhx_small2$co8b)
levels(hhx_small2$co8b)
levels(hhx_small2$co8b) <- c("(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3", "50")
levels(hhy_small2$co8b)
table(hhx_small2$co8b)

hhx_small2$co10b <- factor(hhx_small2$co10b)
levels(hhx_small2$co10b)
levels(hhx_small2$co10b) <- c("0","(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3", "4")
levels(hhy_small2$co10b)
table(hhx_small2$co10b)

unique(hhx_small2$cg1)
hhx_small2$co14b <- factor(hhx_small2$co14b)
levels(hhx_small2$co13b)
levels(hhx_small2$cg1) <- c("(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3", "6", "35")
levels(hhy_small2$cg1)
table(hhx_small2$cg1)

hhx_small2$cg1 <- NULL
hhy_small2$cg1 <- NULL

unique(hhx_small2$db1)
hhx_small2$co14b <- factor(hhx_small2$co14b)
levels(hhx_small2$co13b)
levels(hhx_small2$cg1) <- c("(1) Home grown 1", "(2) Purchased 2",  "(3) Both 3", "6", "35")
levels(hhy_small2$db1)
table(hhx_small2$cg1)

hhx_small2$db1 <- NULL
hhy_small2$db1 <- NULL

hhx_small2$tr1 <- NULL
hhy_small2$tr1 <- NULL


hhx_small2$lc1 <- NULL
hhy_small2$lc1 <- NULL

unique(hhx_small2$wa2)
hhx_small2$wa2 <- factor(hhx_small2$wa2)
levels(hhx_small2$co13b)
levels(hhx_small2$wa2) <- c("(1) outside 1", "(2) inside 2", "3")
levels(hhy_small2$wa2)
table(hhx_small2$wa2)


hhx_small2$wa11b <- NULL
hhy_small2$wa11b <- NULL


unique(hhx_small2$fu5a)
hhx_small2$fu5a <- factor(hhx_small2$fu5a)
levels(hhx_small2$co13b)
levels(hhx_small2$fu5a) <- c("0","(1) Purchase 1", "(2) Collect from own land 2", "(3) Collect from village/other places", "(4) Both (Purchased & collected) 4")
levels(hhy_small2$fu5a)
table(hhx_small2$fu5a)

hhx_small2$jcardapp <- c("(0) No 0")
unique(hhx_small2$jcardapp)
hhx_small2$hq2a <- factor(hhx_small2$hq2a)
levels(hhx_small2$co13b)
levels(hhx_small2$jcardapp) <- c("(0) No 0",  "(1) Yes 1", "4")
levels(hhy_small2$jcardapp)
table(hhx_small2$hq2a)

hhy_small2$stateid <- factor(hhy_small2$stateid)
levels(hhy_small2$stateid)
```


```{r}
sapply(hhx_small2, levels)
```


bind_rows data
```{r}
hh_long2 <- bind_rows(hhx_small2, hhy_small2)
hh_long <- bind_rows(hhx_small3, hhy_small3)

dim(rbind(hhx_small2, hhy_small2))

dim(hh_long2)
dim(hh_long)
```

Deleting the extra variables created
```{r}
hh_long <- hh_long[,-(361:719)]
dim(hh_long)
```

Arranging variables the way they were
```{r}
hh_long <- hh_long[,match(target, names(hh_long))]
head(hh_long)
```


```{r}

setnames(hh_long, names(hh_long), gsub("\\..*", "", x = target))

head(hh_long)
```

# setting income classification variable

```{r}
hh_long$inccat<- cut(hh_long$income, breaks = c(-300000, 0,300000,600000, 900000, 1200000, Inf), labels = c("neg", "ews", "lig", "l-mig", "u-mig", "hig"))
summary(hh_long$inccat)
summary(hh_long$income)
```

```{r}
dim(hh_long)
```

```{r}
summary(hh_long$jcard)
```

