---
title: "Phase 1"
author: "Saurabh"
date: "December 12, 2017"
output: html_document
---

#Importing the data
Since I've the rda file I've used rio::import()

```{r}
library(rio)

ihds2_hh <- import("36151-0002-Data.rda")
class(ihds2_hh)
dim(ihds2_hh)
```

One more beautiful and organised way of checking the data is 
dplyr::glimpse()
```{r}
library(dplyr)

glimpse(ihds2_hh)
```
@Prashant check the variable DISTRICT!!! Our problem is solved.. :)

#District Names & id
So for our reference 
```{r}
dist_2 <- unique(ihds2_hh$DISTRICT)
#The complete list!
dist_2
```



#Checking Variable Names
```{r}
full_names2 <- names(ihds2_hh)
full_names2
arrange_mnames <- full_names2[order(full_names2)]
arrange_mnames
```

#Checking unique States

```{r}
unique(ihds2_hh$STATEID)
```
Variable with such a data can be cumbersome to work with!

#Changing the variable STATEID to something simple
```{r}
ihds2_hh$STATEID <- gsub(".*[a-z|A-Z]\\s", "", ihds2_hh$STATEID) 
#This will coerce the STATEID variable and make it simple for us to use
```
The above function is called a regex function; a lot more thing to learn on it, took me an hour to get the expected result!
```{r}
head(ihds2_hh$STATEID)
ihds2_hh$STATEID <- as.factor(ihds2_hh$STATEID) #Coercing it back to factors
class(ihds2_hh$STATEID)
```

#Checking Unique Districts in the entire set!
```{r}
unique(ihds2_hh$DISTID)

```
@Prashant This is the problem we were facing!
@Rest According to the survey we must have approx 300 districts but we can see only 68

```{r}
#Counting frequncy of each state
table(ihds2_hh$STATEID)
```
Choosing random states to check district codes under it.

```{r}
set2 <- subset(ihds2_hh, STATEID %in% c("02", "03", "08", "21", "28"))
table(st = set2$STATEID, dst = set2$DISTID)
```
From the Table we can see that the District codes are reused!!!

```{r}
summary(ihds2_hh$SURVEY)
```

Correcting the first variable

```{r}
ihds2_hh$SURVEY <- as.character(ihds2_hh$SURVEY)
```

Using gsub to clean the first variable

```{r}
ihds2_hh$SURVEY <- gsub(".*[a-z|A-Z]\\s", "", ihds2_hh$SURVEY)
head(ihds2_hh$SURVEY)
```

We Don't need an extra variable for Geographic identifiers, as they've already been concatenated in IDPSU = State + Dist + PSU and also
IDHH = State + Dist + PSU + HHID + HHSPLITID.

How many Split HH do we have to deal with?
```{r}
table(ihds2_hh$HHSPLITID == 1)
```

What is the average pay of NREGA employee?

```{r}
#UNderstanding few variable before

summary(ihds2_hh$NWKNREGA)
#Number of HH members working for NREGA

summary(ihds2_hh$NWKNONNREGA)
#Number of HH members working for NON NREGA

summary(ihds2_hh$INCNREGA)
#Mean = INR 855


```

#Exploring further into the Income variable
First we need to see how many observations of NREGA employed vs non NREGA
```{r}
summary(ihds2_hh$IN16)
#IN16 is Number of NREGA Jobcards in each HH

ihds2_hh$nrega <- ifelse(ihds2_hh$IN16 > 0, TRUE, FALSE)
#Creating a variable which will help us distinguish between NREGA and NON NREGA

table(ihds2_hh$nrega, useNA = "always")

#Crosschecking with the facts from table
sum(ihds2_hh$IN16 == 0, na.rm = TRUE)

```

So we have 11968 observations of NREGA as compared to Non NREGA which are 30110.
NOTE: These are just observations, the number of employed will be higher than 11968

To Check total number of employed people
```{r}
sum(ihds2_hh$IN16, na.rm = TRUE)
```
Slightly higher than 11968!


```{r}
library(dplyr)
#Data with NREGA employed only
nrega2 <- filter(ihds2_hh, nrega == TRUE)
dim(nrega2)
boxplot(nrega2$INCNREGA)


```

##How many are un-paid employees or employees which were not issued any work!

```{r}
table(nrega2$INCNREGA > 0)
```

```{r}
nonzero <- nrega2[which(nrega2$INCNREGA > 0),]

dim(nonzero)

summary(nonzero$INCNREGA)
```

```{r}
car::Boxplot(nonzero$INCNREGA)
#[1] 2245 2247 2251 2253 2252 2255 2515 3268 2679 1386 are outliers
```

```{r}
#The number of observations which fall beyond INR 10000 as payment for NREGA per month
sum(nonzero$INCNREGA > 20000)
```


```{r}
library(ggplot2)

ggplot(nonzero, aes(x = INCNREGA)) +
  geom_dotplot() 


```

In all, what we can see is in IHDS II is that we've very few proper observation to work with! 

```{r}
#To understand the Number of persons in HH with High Pay!
nonzero[nonzero$INCNREGA > 50000, "NWKNREGA"]
```

@Prashant throw some light on this! 