---
title: "Princomp"
author: "Saurabh"
date: "February 15, 2018"
output: html_document
---
Getting consumption data ready for princomp

Using only consumption variable
```{r}
require(dplyr)
co_data <- hhx_new1 %>%
  select(starts_with("co"), -ends_with("b"), -ends_with("c"), -ends_with("t"), -ends_with("x"), -ends_with("e"), -code, -c(co15:co19), -c(co20:co29), -c(co30:co39), -c(co40:co47))%>%
  bind_cols(copc = x_subset$copc)
co_data

co_data3 <- co_data %>%
  select(-c(co11a, co12a, co1d, co2d, co3d, co5a, co5d, co8a, co9a, copc))

co_data4 <- co_data %>%
  select(co1a, co2a, co3a, co4a, co5a, co7a, co8a, co9a, co10a, co11a, co12a)

co_data4

```



```{r}
pc_co4 <- princomp(formula = ~., data = co_data4, cor = TRUE)

summary(pc_co4)
```

Sending Loadiings to Mentors
```{r}
pc_co4$loadings

```


Understanding the overall distribution of each variable
```{r}
lapply(co_data, desc_stat)
```


```{r}
co_data$co10a <- replace(co_data$co10a, which(is.na(co_data$co10a)), 0)

co_data$co11a <- replace(co_data$co11a, which(is.na(co_data$co11a)), 0)

co_data$co12a <- replace(co_data$co12a, which(is.na(co_data$co12a)), 0)



co_data$co1a <- replace(co_data$co1a, which(is.na(co_data$co1a)), 0)

co_data$co1d <- replace(co_data$co1d, which(is.na(co_data$co1d)), 0)


co_data$co2a <- replace(co_data$co2a, which(is.na(co_data$co2a)), 0)

co_data$co2d <- replace(co_data$co2d, which(is.na(co_data$co2d)), 0)


co_data$co3a <- replace(co_data$co3a, which(is.na(co_data$co3a)), 0)

co_data$co3d <- replace(co_data$co3d, which(is.na(co_data$co3d)), 0)

co_data$co4a <- replace(co_data$co4a, which(is.na(co_data$co4a)), 0)

co_data$co4d <- replace(co_data$co4d, which(is.na(co_data$co4d)), 0)

co_data$co5a <- replace(co_data$co5a, which(is.na(co_data$co5a)), 0)

co_data$co5d <- replace(co_data$co5d, which(is.na(co_data$co5d)), 0)

co_data$co7a <- replace(co_data$co7a, which(is.na(co_data$co7a)), 0)

co_data$co8a <- replace(co_data$co8a, which(is.na(co_data$co8a)), 0)

co_data$co9a <- replace(co_data$co9a, which(is.na(co_data$co9a)), 0)
```


Trying to create a fuction to impute missing values from the entire dataset, imputing it to 0
```{r}
na_index <- function(x) {
  for(i in 1:length(x)) {
    which(is.na(x))
    }
}

replace_na(co_data$co10a)

apply(co_data, 2, replace, na_index, 0)
```
Need to find a robust method which can go through each row of each variable and impute 0

Scaling data
```{r}
scale_co <- as.data.frame(scale(co_data))
scale_ntcopc <- as.data.frame(scale(co_data2))
```


#PrincComp

```{r}
pc_co <- princomp(formula = ~., data = co_data, cor = TRUE)
pc_co

pc_coscale <- princomp(formula = ~., data = scale_co, cor = TRUE)

pc_co2 <- princomp(formula = ~., data = co_data2, cor = TRUE) 

```

```{r}
summary(pc_co)
summary(pc_coscale)
summary(pc_co2)
```

```{r}
cor(co_data)
```

```{r}
cor(co_data3)
```

```{r}
pc_co3 <- princomp(formula = ~., data = co_data3, cor = TRUE)
summary(pc_co3)
```

```{r}
x_subset_clean <- na.omit(x_subset)
dim(x_subset_clean)
```

```{r}
desc_stat(hh_nrega$co1a)
```

```{r}
nrega_co <- hh_nrega %>%
  select(starts_with("co"), -ends_with("b"), -ends_with("c"), -ends_with("t"), -ends_with("x"), -ends_with("e"), -code, -c(co15:co19), -c(co20:co29), -c(co30:co39), -c(co40:co47))
  

sapply(nrega_co, desc_stat)
```

pc_wb_co
```{r}
pc_wb_co <- princomp(formula=~co15 + co16 + co17 + co18 + co19 + co20 + co21 + co22 + co23 + co24 + co25 + co26 + co27 + co28 + co29 + co30 + co31 + co32 + co33 + co34 + co35 + co36 + co37 + co38 + co39 + co40 + co41 + co42 + co43 + co44 + co45 + co46 + co47, data = wb_success, cor = TRUE)
summary(pc_wb_co)
```

