---
title: "Renaming Vars 1.0"
author: "Saurabh"
date: "January 18, 2018"
output: html_document
---
#Working on my file!
```{r}
class(s_vars$new_v)

View(tbl_df(t(s_vars2)))

```

Renaming IHDS2 vars
FM Variables

```{r}
#Need to remove NA's before we aggregate the data
fm_mut <- ihds2_hh %>%
  select(FM4A : FM7C) 

fm_mut[is.na(fm_mut)] <- 0
#Creating one more fm variable just for reference
fm_mut2 <- fm_mut
fm_mut
fm_mut2

  
```
The above step is not needed since we do not aggregate the the 3 variables into 1 var! Specifically for fm4 variable we'd to calculate the total land owned by a HH, so we have used max as the function

```{r}
library(dplyr)

ihds2_hh %>%
  select(FM4A, FM4B, FM4C)


fm_df <- data.frame(FM4A = ihds2_hh$FM4A, FM4B = ihds2_hh$FM4B, 
                    FM4C = ihds2_hh$FM4C)
fm_df$fm4 <- pmax(FM4A = ihds2_hh$FM4A, FM4B = ihds2_hh$FM4B, 
                    FM4C = ihds2_hh$FM4C, na.rm = TRUE)

ihds2_hh$fm4 <- fm_df$fm4


  #select(as.double(fm4), FM4A, FM4B, FM4C)
           
           #pmax(na.rm = TRUE, ihds2_hh %>%
            #          select(FM4A, FM4B, FM4C))) %>%
  #select(fm4, FM4A, FM4B, FM4C)


library(dplyr)
head(as.data.frame(ihds2_hh$FM4A, ihds2_hh$FM4B, ihds2_hh$FM4C))
#head(sapply(, FUN = max, na.rm = TRUE))
ihds2_hh$FM4A



fm4mut <- fm_mut %>%
  mutate(fm4i = (FM4A + FM4B + FM4C)/3) %>%
  select(fm4i) 

dim(fm4)

sum(ihds2_hh$FM4A != fm4$fm4, na.rm = TRUE)

fm4_z <- which(fm_mut$FM4A != fm4mut) 

length(fm4_z)

fm4i <- ihds2_hh %>%
  mutate(fm4i = (FM4A + FM4B + FM4C)/3) %>%
  select(fm4i)

fm4_na <- which(ihds2_hh$FM4A != fm4i$fm4i)
length(fm4_na)

  
diff_fm <- setdiff(fm4_z, fm4_na)
diff_fm

View(ihds2_hh[diff_fm,c("FM4A", "FM4B", "FM4C", "fm4")])


```

###Next variable fm8a == FM5A/5B/5C

```{r}
fm8a <- pmax(ihds2_hh$FM5A, ihds2_hh$FM5B, ihds2_hh$FM5C, na.rm = TRUE)

head(fm8a)
#Testing the variable fm8a
head(which(fm8a > 0))

head(which(is.na(fm8a)))

fm8a_z <- data.frame(fm8a, ihds2_hh$FM5A, ihds2_hh$FM5B, ihds2_hh$FM5C)

fm8a_z[which(fm8a > 0),]

fm8a_z[which(is.na(fm8a)),]
ihds2_hh$fm8a <- fm8a
```

#fm6a variable from FM6A/6B/6C
```{r}
fm6a <- pmax(ihds2_hh$FM6A, ihds2_hh$FM6B, ihds2_hh$FM6C, na.rm = TRUE)

fm6a_z <- data.frame(fm6a, ihds2_hh$FM6A, ihds2_hh$FM6B, ihds2_hh$FM6C)

head(fm6a_z)

head(which(fm6a>0))
#Testing for more than 0 values
fm6a_z[which(fm6a>0),]
#Testing for NA
fm6a_z[which(is.na(fm6a)),]

ihds2_hh$fm6a <- fm6a 

head(ihds2_hh$fm6a)
```

#fm9d
```{r}
ihds2_hh %>%
  select(FM12A, FM12B, FM12C)
```

```{r}
fm9d <- pmax(ihds2_hh$FM12A, ihds2_hh$FM12B, ihds2_hh$FM12C, na.rm = TRUE)

fm9d_z <- data.frame(fm9d, ihds2_hh$FM12A, ihds2_hh$FM12B, ihds2_hh$FM12C)

head(fm9d_z)
#Since we can see both NAs and 0's, no need to test them independently.

ihds2_hh$fm9d <- fm9d
```

```{r}
fm_var <- import("fm_var.xlsx")
fm_var <- tbl_df(fm_var)

glimpse(fm_var)

fm_var$Var_new <- tolower(fm_var$Var_new)
```

```{r}
fm_all2 <- ihds2_hh %>%
  select(starts_with("FM"))

fm_all2

library(data.table)
setnames(fm_all2, fm_var$Var2, fm_var$Var_new)[]

```

Creating a function to rename variables
```{r}
rename_variables <- function(a, y) {
  library(rio)
  library(dplyr)
  library(data.table)
  b <- import(a) %>%
    tbl_df()
  b$Var_new <- tolower(b$Var_new)
  z <- ihds2_hh %>%
    select(starts_with(y))
    setnames(x = z, old = b$Var2, new = b$Var_new)
  z
}
```

```{r}
fu_all2 <- rename_variables(a = "fu_var.xlsx", y = "FU")

fu_all2
```

Checking IN data consistency in all IN type vars
```{r}
head(ihds1_hh$in16a)
```


```{r}
in_all2 <- rename_variables(a = "in_var.xlsx", y = "IN")

in_all2
```

Multi_var, too many variables to bypass the function

```{r}
library(rio)
multi_var <- import("multi_var.xlsx")
multi_var <- tbl_df(multi_var)
multi_var
```

```{r}
multi_var$Var_new <- tolower(multi_var$Var_new)

multi_var
```

```{r}
library(data.table)
multi_all2 <- ihds2_hh %>%
  select(starts_with("DB"), starts_with("ID"), starts_with("GROUPS"), starts_with("TR"), starts_with("LC"), starts_with("HQ"), starts_with("POOR")) %>%
setnames(multi_var$Var2, multi_var$Var_new)
multi_all2

```

#Water
```{r}
wa_all2 <- rename_variables("wa_var.xlsx", y = "WA")
wa_all2
```

#N and Obs

##nchild, nteen variable
```{r}
summary(ihds2_hh$NCHILDF) 
summary(ihds2_hh$NCHILDM)

ihds2_hh$nchild <- ihds2_hh$NCHILDF + ihds2_hh$NCHILDM
summary(ihds2_hh$nchild)

summary(ihds2_hh$NTEENF)
summary(ihds2_hh$NTEENM)
ihds2_hh$nteen <- ihds2_hh$NTEENF + ihds2_hh$NTEENM
summary(ihds2_hh$nteen)

summary(ihds2_hh$NADULTF)
summary(ihds2_hh$NADULTM)
ihds2_hh$nadults <- ihds2_hh$NADULTF + ihds2_hh$NADULTM
summary(ihds2_hh$nadults)

```

Needs manually working on it
```{r}
n_obs_var <- import("n_obs_var.xlsx")
n_obs_var <- tbl_df(n_obs_var)
n_obs_var
```

```{r}
n_obs_var$Var_new <- tolower(n_obs_var$Var_new)
n_obs_var
```


```{r}
n_obs_all2 <- ihds2_hh %>%
  select(starts_with("N"), starts_with("OH"), -starts_with("NF"), 
         -starts_with("NWK"), -nrega) %>%
  setnames(n_obs_var$Var2, n_obs_var$Var_new)

n_obs_all2  
```

#Consumption
```{r}
summary(ihds2_hh$CO16)
summary(ihds2_hh$CO17)


ihds2_hh$co16 <- ihds2_hh$CO16 + ihds2_hh$CO17

summary(ihds2_hh$co16)

summary(ihds2_hh$CO20)
summary(ihds2_hh$CO21)
ihds2_hh$co20 <- ihds2_hh$CO20 + ihds2_hh$CO21
summary(ihds2_hh$co20)

summary(ihds2_hh$CO26)
summary(ihds2_hh$CO27)
ihds2_hh$co25 <- ihds2_hh$CO26 + ihds2_hh$CO27 
summary(ihds2_hh$co25)

summary(ihds2_hh$CO30)
summary(ihds2_hh$CO30B)
ihds2_hh$co27 <- ihds2_hh$CO30 + ihds2_hh$CO30B 
summary(ihds2_hh$co27)

summary(ihds2_hh$CO35)
summary(ihds2_hh$CO36)
ihds2_hh$co32 <- ihds2_hh$CO35 + ihds2_hh$CO36 
summary(ihds2_hh$co32)
```

```{r}
co_all2 <- rename_variables("co_var.xlsx", "CO")
co_all2
```

#Assets
```{r}
unique(ihds2_hh$ASSETS)
summary(ihds2_hh$ASSETS)

summary(ihds1_hh$HHASSETS)

summary(ihds2_hh$ASSETS2005)
```

```{r}
ihds2_hh$assets <- ihds2_hh$ASSETS
```

```{r}
cg_all2 <- rename_variables("cg_var.xlsx", "CG")
cg_all2
```


```{r}
unique(ihds1_hh$RC1)


table(ihds1_hh$RC1)
ihds1_hh$RC1 <- ifelse(ihds1_hh$RC1 == 1, TRUE, FALSE)

ihds2_hh$RC1 <- ifelse(ihds2_hh$RC1 == "(1) Yes 1", TRUE, FALSE)

summary(ihds1_hh$RC1)
summary(ihds2_hh$RC1)

unique(ihds2_hh$RC1)
```

```{r}
unique(ihds1_hh$RC1A)

unique(ihds2_hh$RC1A)
```

```{r}
ihds1_hh$RC1A <- ifelse(ihds1_hh$RC1A == "(1) BPL", "BPL", 
                        ifelse(ihds1_hh$RC1A == "(3) Antodaya", "Antodaya", ifelse(ihds1_hh$RC1A == "(2) Standard/APL","Standard/APL", ifelse(ihds1_hh$RC1A == "NA", "NA", "Annapurna" ))))

ihds1_hh$RC1A <- factor(ihds1_hh$RC1A)

summary(ihds1_hh$RC1A)
```

```{r}
ihds2_hh$rc1a <- ifelse(ihds2_hh$RC1B1 == "(1) Yes", "BPL", 
                        ifelse(ihds2_hh$RC1B3 == "(1) Yes", "Antodaya", ifelse(ihds2_hh$RC1B2 == "(1) Yes","Standard/APL", ifelse(ihds2_hh$RC1B4 == "(1) Yes", "Annapurna","NA" ))))

length(ihds2_hh$rc1a)

ihds2_hh$rc1a <- factor(ihds2_hh$rc1a)
summary(ihds2_hh$rc1a)
```

```{r}
hh_rc_var <- import("hh_rc_var.xlsx")
hh_rc_var
```

```{r}
hh_rc_var$Var_new <- tolower(hh_rc_var$Var_new)
hh_rc_var
```

```{r}
hh_rc_all2 <- ihds2_hh %>%
  select(starts_with("HHEDUC"), starts_with("RC")) %>%
  setnames(hh_rc_var$Var2, hh_rc_var$Var_new)
```

```{r}
hh_rc_all2
```

#Non Farming

```{r}
nf_all2 <- rename_variables("nf_var.xlsx", "NF")
nf_all2
```

#Animals
```{r}
an_all2 <- rename_variables("an_var.xlsx", "AN")
an_all2
```

#Membership
```{r}
me_all2 <- rename_variables("me_var.xlsx", "ME")
me_all2
```

#Marriage Practices
```{r}
mp_all2 <- rename_variables("mp_var.xlsx", "MP")
mp_all2
```

#Sanitation
```{r}
unique(ihds1_hh$SA2A)
table(ihds1_hh$SA2A)
unique(ihds2_hh$SA2A)
```
Not using SA2A variable in the joint data frame.

```{r}
sa_all2 <- rename_variables("sa_var.xlsx", "SA")
sa_all2
```

#Employment
```{r}
ihds1_hh$NWKNREGA <- 0

ihds1_hh$NWKNONNREGA <- 0
```


```{r}
emp_all2 <- rename_variables("emp_var.xlsx", "NWK")
emp_all2
```

Changing the variable names to lower case in IHDS 1
```{r}
setnames(ihds1_hh, names(ihds1_hh), tolower(names(ihds1_hh)))
head(ihds1_hh)
```

```{r}
cng_id_var <- import("cng_id_var.xlsx")
cng_id_var <- tbl_df(cng_id_var)

cng_id_var$Var_new <- tolower(cng_id_var$Var_new)
cng_id_var
```

```{r}
cng_all2 <- ihds2_hh %>%
  select(SURVEY:IDHH, DIST01, METRO6, URBAN2011, sid, nrega, assets) %>%
  setnames(cng_id_var$Var2, cng_id_var$Var_new)
cng_all2
```


```{r}
unique(ihds2_hh$URBAN2011)

unique(ihds2_hh$URBAN4_2011)

unique(ihds1_hh$urban)

```


Summary:
1.) So far we've renamed FM, FU, IN, INC, DB, ID, GROUPS, TR, LC, HQ, POOR, WA, N, OH, CO, ASSETS, CG, RC, HHED, NF, AN, ME, MP,
SA, NWORK, C & G Id type.
2.) In addition to this we'll require survey, sid, distid, psuid, hhid, hhsplitid, code, nrega, assets for the combined dataset.  