---
title: "rework2_checking_classes & levels"
author: "Saurabh"
date: "February 2, 2018"
output: html_document
---
```{r}
library(rio)

hhx_new <- import("hhx_new.rda")

hhy_new <- import("hhy_new.rda")

hhx_new <- tbl_df(hhx_new)

hhy_new <- tbl_df(hhy_new)

```

Checking parity of classes
```{r}
sapply(hhy_new, class)
sapply(hhx_new, class)
```

Working on the anomalies
CG1
```{r}
unique(hhx_new$cg1)
unique(hhy_new$cg1)
table(hhx_new$cg1)
summary(hhx_new$cg1)
summary(hhy_new$cg1)

#Removing 100 and coercing it too NA
```

```{r}
library(car)
hhx_new$cg1 <- recode(hhx_new$cg1, "100=NA")
#Checking again
table(hhx_new$cg1)
```
Voila!

Similarly
```{r}
hhy_new$cg1 <- recode(hhy_new$cg1, "'(1) Owned 1' = 1; '(2) Rented 2' = 2; NA = NA; else = 3")

summary(hhy_new$cg1)
```

CO10B
```{r}
unique(hhx_new$co10b)
unique(hhy_new$co10b)
table(hhx_new$co10b)
summary(hhx_new$co10b)
summary(hhy_new$co10b)
```

Removing 0s and NAs
```{r}
hhx_new$co10b <- recode(hhx_new$co10b, "0 = NA; 4 = NA")
#Checking again
table(hhx_new$co10b)
```

Similarly
```{r}
hhy_new$co10b <- recode(hhy_new$co10b, "'(1) Home grown 1' = 1; '(2) Purchased 2' = 2;'(3) Both 3' = 3")
#Checking again
table(hhy_new$co10b)
```

CO11b
```{r}
unique(hhx_new$co11b)
unique(hhy_new$co11b)
table(hhx_new$co11b)
summary(hhx_new$co11b)
summary(hhy_new$co11b)
```

removing 22
```{r}
hhx_new$co11b <- recode(hhx_new$co11b,"22=NA" )
#Checking again
table(hhx_new$co11b)
class(hhx_new$co11b)
hhx_new$co11b <- factor(hhx_new$co11b)
levels(hhx_new$co11b)
```
Releveling
```{r}
levels(hhx_new$co11b) <- levels(hhy_new$co11b)
table(hhx_new$co11b)
```

co12b
```{r}
unique(hhx_new$co12b)
unique(hhy_new$co12b)
table(hhx_new$co12b)
summary(hhx_new$co12b)
summary(hhy_new$co12b)
```
Removing 40
```{r}
hhx_new$co12b <- recode(hhx_new$co12b,"40=NA" )
#Checking again
table(hhx_new$co12b)
class(hhx_new$co12b)
hhx_new$co12b <- factor(hhx_new$co12b)
levels(hhx_new$co12b)
```

```{r}
levels(hhx_new$co12b) <- levels(hhy_new$co12b)
table(hhx_new$co12b)
```

co13b
```{r}
unique(hhx_new$co13b)
unique(hhy_new$co13b)
table(hhx_new$co13b)
summary(hhx_new$co13b)
summary(hhy_new$co13b)
```

removing 0s
```{r}
hhx_new$co13b <- recode(hhx_new$co13b,"0=NA" )
#Checking again
table(hhx_new$co13b)
class(hhx_new$co13b)
hhx_new$co13b <- factor(hhx_new$co13b)
levels(hhx_new$co12b)
#Matching it with dat 2
levels(hhx_new$co12b) <- levels(hhy_new$co12b)
table(hhx_new$co12b)
```

co14b
```{r}
unique(hhx_new$co14b)
unique(hhy_new$co14b)
table(hhx_new$co14b)
summary(hhx_new$co14b)
summary(hhy_new$co14b)
```

Removing 6 and 35
```{r}
hhx_new$co14b <- recode(hhx_new$co14b,"6=NA; 35=NA" )
#Checking again
table(hhx_new$co14b)
class(hhx_new$co14b)
hhx_new$co14b <- factor(hhx_new$co14b)
summary(hhx_new$co14b)
#Matching it with dat 2
levels(hhx_new$co14b) <- levels(hhy_new$co14b)
table(hhx_new$co14b)
```

co1b
```{r}
unique(hhx_new$co1b)
unique(hhy_new$co1b)
table(hhx_new$co1b)
summary(hhx_new$co1b)
summary(hhy_new$co1b)
```

removing 15
```{r}
hhx_new$co1b <- recode(hhx_new$co1b,"15=NA" )
#Checking again
table(hhx_new$co1b)
class(hhx_new$co1b)
hhx_new$co1b <- factor(hhx_new$co1b)
summary(hhx_new$co1b)
#Matching it with dat 2
levels(hhx_new$co1b) <- levels(hhy_new$co1b)
table(hhx_new$co1b)
```

co2b
```{r}
unique(hhx_new$co2b)
unique(hhy_new$co2b)
table(hhx_new$co2b)
summary(hhx_new$co2b)
summary(hhy_new$co2b)
```

removing 30 and 0
```{r}
hhx_new$co2b <- recode(hhx_new$co2b,"0=NA; 30=NA" )
#Checking again
table(hhx_new$co2b)
class(hhx_new$co2b)
hhx_new$co2b <- factor(hhx_new$co2b)
summary(hhx_new$co2b)
#Matching it with dat 2
levels(hhx_new$co2b) <- levels(hhy_new$co2b)
table(hhx_new$co2b)
```

co5b
```{r}
unique(hhx_new$co5b)
unique(hhy_new$co5b)
table(hhx_new$co5b)
summary(hhx_new$co5b)
summary(hhy_new$co5b)
```

removing 0
```{r}
hhx_new$co5b <- recode(hhx_new$co5b,"0=NA" )
#Checking again
table(hhx_new$co5b)
class(hhx_new$co5b)
hhx_new$co5b <- factor(hhx_new$co5b)
summary(hhx_new$co5b)
#Matching it with dat 2
levels(hhx_new$co5b) <- levels(hhy_new$co5b)
table(hhx_new$co5b)
```

co7b
```{r}
unique(hhx_new$co7b)
unique(hhy_new$co7b)
table(hhx_new$co7b)
summary(hhx_new$co7b)
summary(hhy_new$co7b)
```

removing 4
```{r}
hhx_new$co7b <- recode(hhx_new$co7b,"4=NA" )
#Checking again
table(hhx_new$co7b)
class(hhx_new$co7b)
hhx_new$co7b <- factor(hhx_new$co7b)
summary(hhx_new$co7b)
#Matching it with dat 2
levels(hhx_new$co7b) <- levels(hhy_new$co7b)
table(hhx_new$co7b)
```

co8b
```{r}
unique(hhx_new$co8b)
unique(hhy_new$co8b)
table(hhx_new$co8b)
summary(hhx_new$co8b)
summary(hhy_new$co8b)
```

Removing 50
```{r}
hhx_new$co8b <- recode(hhx_new$co8b,"50=NA" )
#Checking again
table(hhx_new$co8b)
class(hhx_new$co8b)
hhx_new$co8b <- factor(hhx_new$co8b)
summary(hhx_new$co8b)
#Matching it with dat 2
levels(hhx_new$co8b) <- levels(hhy_new$co8b)
table(hhx_new$co8b)
```

fu5a
```{r}
unique(hhx_new$fu5a)
unique(hhy_new$fu5a)
table(hhx_new$fu5a)
summary(hhx_new$fu5a)
summary(hhy_new$fu5a)
```
removing 0 and coercing ti factor as well as renaming the levels

```{r}
hhx_new$fu5a <- recode(hhx_new$fu5a,"0=NA" )
#Checking again
table(hhx_new$fu5a)
class(hhx_new$fu5a)
hhx_new$fu5a <- factor(hhx_new$fu5a)
summary(hhx_new$fu5a)
#Matching it with dat 2
levels(hhx_new$fu5a) <- levels(hhy_new$fu5a)
table(hhx_new$fu5a)
```

fu7a
```{r}
unique(hhx_new$fu7a)
unique(hhy_new$fu7a)
table(hhx_new$fu7a)
summary(hhx_new$fu7a)
summary(hhy_new$fu7a)
```

```{r}
hhx_new$fu7a <- recode(hhx_new$fu7a,"0=NA" )
#Checking again
table(hhx_new$fu7a)
class(hhx_new$fu7a)
hhx_new$fu7a <- factor(hhx_new$fu7a)
summary(hhx_new$fu7a)
#Matching it with dat 2
levels(hhx_new$fu7a) <- levels(hhy_new$fu7a)
table(hhx_new$fu7a)
```

fu9a
```{r}
unique(hhx_new$fu9a)
unique(hhy_new$fu9a)
table(hhx_new$fu9a)
summary(hhx_new$fu9a)
summary(hhy_new$fu9a)
```

```{r}
hhx_new$fu9a <- recode(hhx_new$fu9a,"0=NA" )
#Checking again
table(hhx_new$fu9a)
class(hhx_new$fu9a)
hhx_new$fu9a <- factor(hhx_new$fu9a)
summary(hhx_new$fu9a)
#Matching it with dat 2
levels(hhx_new$fu9a) <- levels(hhy_new$fu9a)
table(hhx_new$fu9a)
```

groups8
```{r}
unique(hhx_new$groups8)
unique(hhy_new$groups8)
table(hhx_new$groups8)
summary(hhx_new$groups8)
summary(hhy_new$groups8)
class(hhx_new$groups8)
class(hhy_new$groups8)
```

```{r}
hhx_new$groups8 <- factor(hhx_new$groups8)
```

hq2a
```{r}
unique(hhx_new$hq2a)
unique(hhy_new$hq2a)
table(hhx_new$hq2a)
summary(hhx_new$hq2a)
summary(hhy_new$hq2a)
```

removing 4 and changing class & renaming the levels
```{r}
hhx_new$hq2a <- recode(hhx_new$hq2a,"4=NA" )
#Checking again
table(hhx_new$hq2a)
class(hhx_new$hq2a)
hhx_new$hq2a <- factor(hhx_new$hq2a)
summary(hhx_new$hq2a)
#Matching it with dat 2
levels(hhx_new$hq2a) <- levels(hhy_new$hq2a)
table(hhx_new$hq2a)
```

idhh
```{r}
class(hhx_new$idhh)
class(hhy_new$idhh)
```

```{r}
hhy_new$idhh <- as.numeric(hhy_new$idhh)
```

jcardapp
```{r}
unique(hhx_new$jcardapp)
unique(hhy_new$jcardapp)
table(hhx_new$jcardapp)
summary(hhx_new$jcardapp)
summary(hhy_new$jcardapp)
```

coercing 0 to (0) No 0
```{r}
hhx_new$jcardapp <- recode(hhx_new$jcardapp, "0 = '(0) No 0'")
hhx_new$jcardapp <- factor(hhx_new$jcardapp)
table(hhx_new$jcardapp)
sum(is.na(hhx_new$jcardapp))
summary(hhx_new$jcardapp)
```

```{r}
levels(hhx_new$jcardapp) <- levels(hhy_new$jcardapp)
summary(hhx_new$jcardapp)
```

lc1
```{r}
unique(hhx_new$lc1)
unique(hhy_new$lc1)
table(hhx_new$lc1)
summary(hhx_new$lc1)
summary(hhy_new$lc1)
```

Remving 3
```{r}
hhx_new$lc1 <- recode(hhx_new$lc1,"3=NA" )
#Checking again
table(hhx_new$lc1)
class(hhx_new$lc1)
hhx_new$lc1 <- factor(hhx_new$lc1)
summary(hhx_new$lc1)
#Matching it with dat 2
levels(hhx_new$lc1) <- levels(hhy_new$lc1)
table(hhx_new$lc1)
```

tr1
```{r}
unique(hhx_new$tr1)
unique(hhy_new$tr1)
table(hhx_new$tr1)
summary(hhx_new$tr1)
summary(hhy_new$tr1)
```

removing 0
```{r}
hhx_new$tr1 <- recode(hhx_new$tr1,"0=NA" )
#Checking again
table(hhx_new$tr1)
class(hhx_new$tr1)
hhx_new$tr1 <- factor(hhx_new$tr1)
summary(hhx_new$tr1)
#Matching it with dat 2
levels(hhx_new$tr1) <- levels(hhy_new$tr1)
table(hhx_new$tr1)
```

wa11b
```{r}
unique(hhx_new$wa11b)
unique(hhy_new$wa11b)
table(hhx_new$wa11b)
summary(hhx_new$wa11b)
summary(hhy_new$wa11b)
```

removing 0
```{r}
hhx_new$wa11b <- recode(hhx_new$wa11b,"0=NA" )
#Checking again
table(hhx_new$wa11b)
class(hhx_new$wa11b)
hhx_new$wa11b <- factor(hhx_new$wa11b)
summary(hhx_new$wa11b)
#Matching it with dat 2
levels(hhx_new$wa11b) <- levels(hhy_new$wa11b)
table(hhx_new$wa11b)
```

wa2
```{r}
unique(hhx_new$wa2)
unique(hhy_new$wa2)
table(hhx_new$wa2)
summary(hhx_new$wa2)
summary(hhy_new$wa2)
```
Removing 3
```{r}
hhx_new$wa2 <- recode(hhx_new$wa2,"3=NA" )
#Checking again
table(hhx_new$wa2)
class(hhx_new$wa2)
hhx_new$wa2 <- factor(hhx_new$wa2)
summary(hhx_new$wa2)
#Matching it with dat 2
levels(hhx_new$wa2) <- levels(hhy_new$wa2)
table(hhx_new$wa2)
```

